Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-11-18 inst/doc/nonparametric-bayes.Rmd
writing

@@

@@

Model uncertainty is particularly insidious when model predictions
must be made outside of the range of data on which the model was estimated.

An additional source of uncertainty that has recieved less attention[^1]
arises when applying a dynamical model outside the range of data on
which it has been estimated.  This extrapolation uncertainty is felt
most keenly in decision-theoretic applications, as (a) exploring the
potential action space typically involves considering actions that
may move the system outside the range of observed behavior, and (b)
decision-theoretic alogrithms rely not only on reasonable estimates of
the expected outcomes, but depend on the weights given to all possible
outcomes [_e.g._ @Weitzman2013].

<!-- 
## Why we don't know the model
- Complex dynamics  [@Glaser2013](http://doi.org/10.1111/faf.12037 "Complex dynamics may limit prediction in marine fisheries")
- model choice and model averaging approaches
-->

<!--
## Why we don't have data where we need it
- Concerns of tipping points 
- Danger of learning 
-->

<!-- Perhaps this is a better-worded version of the above??

Often the set of feasible states is larger than the range of the observed
states.  Though most systems subject to some degree of stochasticity
can enter a state outside previously observed values by chance alone
(such as a particularly low or high nutrient year), this concern is
most keenly felt in the decision-theoretic context. If we are observing
the fluctuations of a given fish stock over many years under a fixed
harvesting pressure, we might develop and test a model that could
reasonably predict the frequency of a deviation of a given size, even
when such a deviation has not been previously observed.
(The same analogy might be made to predicting hurricanes or other
extreme weather events from historical data, which may be more accurately
predicted in a constant climate than in one being perturbed).

-->

<!-- Does this belong?  Improve transitions -->

Concerns over the potential for tipping points in ecological dynamics
[@Scheffer2001] highlight the dangers of uncertainty in ecological
management and pose a substantial challenge to existing decision-theoretic
approaches [@Brozovic2011].  Because intervention is often too late 
after a tipping point has been crossed (but see @Hughes2013), management
is most often concerned with avoiding potentially catastrophic tipping
points before any data is available at or following a transition that
would more clearly reveal these regime shift dynamics [e.g. @Bestelmeyer2012].

@@

<!-- More consise versions are now above 
#### Parametric uncertainty

#### Structural uncertainty

#### Limits of state space

Resource management and conservation planning seek to determine the
optimal set of feasible actions to maximize the value of some objectives
(see [@Halpern2012])  Process error, measurement error, implementation
error [@Reed1979, @Clark1986, @Roughgarden1996, @Sethi2005].  These
sources of stochasticity in turn mean that model parameters can only
be estimated approximately, requiring parametric uncertainty also be
considered [@Ludwig1982, ].
-->

@@

- Note on: Why fisheries

The economic value and ecological concern have made marine
fisheries the crucible for much of the founding work [@Gordon1954;
@Reed1979; @May1979; @Ludwig1982] in managing ecosystems under
uncertainty.  Global trends [@Worm2006] and controversy [@Hilborn2007;
@Worm2009] have made understanding these challenges all the more pressing.

<!--move to  much later *Or do we need this at all?* -->

- _Note on comparing models_ (via value function rather than by "fit").

@@

The essence of the GP approach can be captured in the following
thought experiment: An exhaustive parametric approach to the challenge
of structural uncertainty might proceed by writing down all possible
functional forms for the underlying dynamical system with all possible
parameter values for each form, and then consider searching over this
huge space to select the most likely model and parameters; or using a
Bayesian approach, assign priors to each of these possible models and
infer the posterior distribution of possible models. The GP approach
can be thought of as a computationally efficient approximation to this
approach. GPs represent a large class of models that can be though
of as capturing or reasonably approximating the set of models in this
collection.  By modeling at the level of the process, rather than the
level of parametric equation, we can more concisely capture the possible
behavior of these curves.  In place of a parametric model of the dynamical
system, the GP approach postulates a prior distribution of (n-dimensional)
curves that can be though of as approximations to a range of possible
(parametric) models that might describe the data. The GP allows us to
consider probabilities on a large set of possible curves simultaneously.

@@

<!-- FIXME -->

- Underlying model 
- Available data

<!--
- Value function
-->

For simplicity we assume profit is simply linear in the realized harvest (only
enforcing the restriction that harvest can not exceed available stock)

@@

We consider three candidate parametric models of the stock-recruitment
dynamics: The Ricker model, the Allen model [Allen 2005](), the Myers
model. The familiar Ricker model involves two parameters, corresponding
to a growth rate and a carrying capacity, and cannot support alternative
stable state dynamics (though as growth rate increases it exhibits a
periodic attractor that proceeds through period-doubling into chaos. We
will generally focus on dynamics below the chaotic threshold for
the purposes of this analysis.) The Allen model resembles the Ricker
dynamics with an added Allee effect parameter [Courchamp](), below
which the population cannot persist.  The Myers model also has three
parameters and contains an Allee threshold, but has compensatory rather
than over-compensatory density dependence (resembling a Beverton-Holt
curve rather than a Ricker curve at high densities.)

@@

As we simulate training data from the Allen model (ref section), we will
refer to this as the structurally correct model.  The Ricker model is
thus a reasonable approximation of these dynamics far from the Allee
threshold (but lacks threshold dynamics), while the Myers model shares
the essential feature of a threshold but differs in the structure. Thus
we have three potential parametric models of the stock dynamics.

@@

```{r deviances, dependson=c("dic_calc"), include=TRUE, results="asis", echo=FALSE}
```

@@

```{r out_of_sample_predictions, include=TRUE, echo=FALSE, fig.width=8, fig.height=6}
```

>>>>

We develop these concerns in the context of fisheries, though
the underlying challenges and methods are germane to many other
conservation and resource management problems.  The economic value and
ecological concern have made marine fisheries the crucible for much
of the founding work [@Gordon1954; @Reed1979; @May1979; @Ludwig1982]
in managing ecosystems under uncertainty.  Global trends [@Worm2006]
and controversy [@Hilborn2007; @Worm2009] have made understanding these
challenges all the more pressing.

@@

_Cut the next three paragraphs, since they are covered more consisely in the above paragraph?_

#### Process, measurement, and implementation error

Resource management and conservation planning seek to determine the
optimal set of feasible actions to maximize the value of some objectives
(see [@Halpern2012]).  Process error, measurement error, implementation
error [@Reed1979, @Clark1986, @Roughgarden1996, @Sethi2005].  These
sources of stochasticity in turn mean that model parameters can only
be estimated approximately, requiring parametric uncertainty also be
considered [@Ludwig1982].

#### Parametric uncertainty

#### Structural (model) uncertainty

@@

Model uncertainty is particularly insidious when model predictions must
be made outside of the range of data on which the model was estimated.
This extrapolation uncertainty is felt most keenly in decision-theoretic
(or optimal control) applications, since (a) exploring the potential
action space typically involves considering actions that may move the
system outside the range of observed behavior, and (b) decision-theoretic
alogrithms rely not only on reasonable estimates of the expected
outcomes, but depend on the weights given to all possible outcomes
[_e.g._ @Weitzman2013].  If we are observing the fluctuations of a
given fish stock over many years under a fixed harvesting pressure,
we might develop and test a model that could reasonably predict the
frequency of a deviation of a given size, even when such a deviation has
not been previously observed. Yet such predictions are far less reliable
when extrapolated to a harvest pressure that has not yet been observed.
Thus, model uncertainty can be particularly challenging in the management
and decision-making context.

This difficult position of having neither the true model nor data that
covers the full range of possible states is unfortunately the rule more
than the exception. The potential concern of tipping points in ecological
dyanmics [@Scheffer2001; @Polasky2011] reflects these concerns -- as
either knowledge of the true model or more complete sampling of the
state space would make it easy to identify if a tipping point existed.
If we do not know but cannot rule out such a possibility, then we
face decision-making under this dual challege of model uncertainty and
incomplete data coverage.

These dual concerns pose a substantial challenge to existing decision-theoretic
approaches [@Brozovic2011].  Because intervention is often too late 
after a tipping point has been crossed (but see @Hughes2013), management
is most often concerned with avoiding potentially catastrophic tipping
points before any data is available at or following a transition that
would more clearly reveal these regime shift dynamics [e.g. @Bestelmeyer2012].

@@

@@

<!--move to  much later *Or do we need this at all?* 
- _Note on comparing models_ (via value function rather than by "fit"). 
-->

@@

<!-- Useless 
The essence of the GP approach can be captured in the following
thought experiment: An exhaustive parametric approach to the challenge
of structural uncertainty might proceed by writing down all possible
functional forms for the underlying dynamical system with all possible
parameter values for each form, and then consider searching over this
huge space to select the most likely model and parameters; or using a
Bayesian approach, assign priors to each of these possible models and
infer the posterior distribution of possible models. The GP approach
can be thought of as a computationally efficient approximation to this
approach. GPs represent a large class of models that can be though
of as capturing or reasonably approximating the set of models in this
collection.  By modeling at the level of the process, rather than the
level of parametric equation, we can more concisely capture the possible
behavior of these curves.  In place of a parametric model of the dynamical
system, the GP approach postulates a prior distribution of (n-dimensional)
curves that can be though of as approximations to a range of possible
(parametric) models that might describe the data. The GP allows us to
consider probabilities on a large set of possible curves simultaneously.
-->

@@

To illustrate the application of the BNP-SDP approach and compare to the
predictions of the alternative parametric models we focus on the classical
problem of selecting the appropriate harvest level given an observation
of the stock size in the previous year  [@Reed1979; @Walters1982, @Mangel1988].
Given this observation and the model (together with the parameter uncertainty) of the stock
recruitment process, the manager seeks to maximize the value of the 
fishery over a fixed time interval of `r OptTime` years at a discount rate
of `r delta`. The value function (profits) at time $t$ depends on the true stock size
$x_t$ and the chosen harvest level $h_t$.  For simplicity we assume profit 
is simply proportional in the realized harvest (only
enforcing the restriction that harvest can not exceed available stock).

@@

We consider three candidate parametric models of the stock-recruitment
dynamics: The Ricker model, the Allen model [@Allen2005], the Myers
model [@Myers1995]. The familiar Ricker model involves two parameters, corresponding
to a growth rate and a carrying capacity, and cannot support alternative
stable state dynamics (though as growth rate increases it exhibits a
periodic attractor that proceeds through period-doubling into chaos. We
will generally focus on dynamics below the chaotic threshold for
the purposes of this analysis.) The Allen model resembles the Ricker
dynamics with an added Allee effect parameter [@Courchamp2008], below
which the population cannot persist.  The Myers model also has three
parameters and contains an Allee threshold, but has compensatory rather
than over-compensatory density dependence (resembling a Beverton-Holt
curve rather than a Ricker curve at high densities.)

@@

As we simulate training data from the Allen model, we will
refer to this as the structurally correct model.  The Ricker model is
thus a reasonable approximation of these dynamics far from the Allee
threshold (but lacks threshold dynamics), while the Myers model shares
the essential feature of a threshold but differs in the structure. Thus
we have three potential parametric models of the stock dynamics.

We introduce parameteric uncertainty by first estimating each of the
candidate models from data on unexploited stock dynamics following
some pertubation (non-equilibrium initial condition) over several time
steps. This training data could be generated in several different ways
(such as known variable exploitation rates, etc), as long as it reflects
the dynamics in some limited region of state space without impacting
the problem.  We consider a period of `r Tobs` years of training data: long
enough that the estimates are not dependent on the particular realization,
while longer times are not likely to provide substantial improvement
(i.e. the results are not sensitive to this interval).  Each of the models
(described below) is fit to the same training data, as shown in Figure 1.

@@

```{r deviances, dependson=c("dic_calc"), include=FALSE, echo=FALSE}
```

```{r Table1, dependson="deviances", include=TRUE, results="asis", echo=FALSE}
xtable::xtable(rbind(dictable, aictable, bictable))
```

@@

```{r out_of_sample_predictions, include=TRUE, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Out of sample predictions of the dynamics under each model.  Points show the stock size simulated by the true model.  Overlay shows the range of states predicted by each model, based on the state observed in the previous time step. The Ricker model always predicts population growth, while the actual population shrinks in each step as the initial condition falls below the Allee threshold of the underlying model (Allen).  Note that the GP is both more pessimistic and more uncertain about the future state than the parameteric models, while the realized state often falls outside of the expected range forecasted by the structurally incorrect Myers and Ricker models." }
```

### 2013-11-18 inst/doc/nonparametric-bayes.tex
writing

Uncertainty enters the decision-making process at many levels: intrinsic
stochasticity in biological processes, measurements, and implementation
of policy (\emph{e.g.} Reed 1979; C. W. Clark and Kirkwood 1986;
Roughgarden and Smith 1996; Sethi et al. 2005), parameteric uncertainty
(\emph{e.g.} Ludwig and Walters 1982; Hilborn and Mangel 1997;
McAllister 1998; Schapaugh and Tyre 2013), and model or structural
uncertainty (\emph{e.g.} B. K. Williams 2001; Cressie et al. 2009;
Athanassoglou and Xepapadeas 2012). Of these, structural uncertainty
incorporates the least a priori knowledge or assumptions and is
generally the hardest to quantify. Typical approaches assume a weak
notion of model uncertainty in which the correct model (or reasonable
approximation) of the dynamics must be identified from among a handful
of alternative models. Here we consider an approach that addresses
uncertainty at each of these levels without assuming the dynamics follow
a particular (i.e.~parametric) structure.

Model uncertainty is particularly insidious when model predictions must
be made outside of the range of data on which the model was estimated.

An additional source of uncertainty that has recieved less
attention{[}\^{}1{]} arises when applying a dynamical model outside the
range of data on which it has been estimated. This extrapolation
uncertainty is felt most keenly in decision-theoretic applications, as
(a) exploring the potential action space typically involves considering
actions that may move the system outside the range of observed behavior,
and (b) decision-theoretic alogrithms rely not only on reasonable
estimates of the expected outcomes, but depend on the weights given to
all possible outcomes (\emph{e.g.} Weitzman 2013).

Concerns over the potential for tipping points in ecological dynamics
(Scheffer et al. 2001) highlight the dangers of uncertainty in
ecological management and pose a substantial challenge to existing
decision-theoretic approaches (Brozović and Schlenker 2011). Because
intervention is often too late after a tipping point has been crossed
(but see Hughes et al. (2013)), management is most often concerned with
avoiding potentially catastrophic tipping points before any data is
available at or following a transition that would more clearly reveal
these regime shift dynamics (e.g. Bestelmeyer et al. 2012).

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Note on: Why fisheries
\end{itemize}

The economic value and ecological concern have made marine fisheries the
crucible for much of the founding work (H. S. Gordon 1954; Reed 1979;
May et al. 1979; Ludwig and Walters 1982) in managing ecosystems under
uncertainty. Global trends (Worm et al. 2006) and controversy (Hilborn
2007; Worm et al. 2009) have made understanding these challenges all the
more pressing.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \emph{Note on comparing models} (via value function rather than by
  ``fit'').
\end{itemize}

@@

This non-parametric property -- having a structure explicitly dependent
on the data -- is precisely the property that makes this approach
attractive in face of the limited data sampling challenges discussed
above. Having fit a parametric model to some data, the model is
completely described by the values (or posterior distributions) of it's
parameters. The non-parametric model is not captured by its parameter
values or distributions alone. Either the model scales with the
complexity of the data on which it is estimated (e.g.~nonparametric
heirarchical approaches such as the Dirchlet process) or the data points
become themselves part of the model specification, as in the
nonparametric regression used here. we shall see here.

The use of Gaussian process (GP) regression (or ``kriging'' in the
geospatial literature) to formulate a predictive model is relatively new
in the context of modeling dynamical systems (Kocijan et al. 2005), and
was first introduced in the context ecological modeling and fisheries
management in Munch et al. (2005). An accessible and thorough
introduction to the formulation and use of GPs can be found in Rasmussen
and Williams (2006).

The essence of the GP approach can be captured in the following thought
experiment: An exhaustive parametric approach to the challenge of
structural uncertainty might proceed by writing down all possible
functional forms for the underlying dynamical system with all possible
parameter values for each form, and then consider searching over this
huge space to select the most likely model and parameters; or using a
Bayesian approach, assign priors to each of these possible models and
infer the posterior distribution of possible models. The GP approach can
be thought of as a computationally efficient approximation to this
approach. GPs represent a large class of models that can be though of as
capturing or reasonably approximating the set of models in this
collection. By modeling at the level of the process, rather than the
level of parametric equation, we can more concisely capture the possible
behavior of these curves. In place of a parametric model of the
dynamical system, the GP approach postulates a prior distribution of
(n-dimensional) curves that can be though of as approximations to a
range of possible (parametric) models that might describe the data. The
GP allows us to consider probabilities on a large set of possible curves
simultaneously.

@@

\% latex table generated in R 3.0.2 by xtable 1.7-1 package \% Thu Nov
14 14:10:28 2013

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/nonparametric-bayes-out_of_sample_predictions.pdf}
\caption{plot of chunk out\_of\_sample\_predictions}
\end{figure}

@@

Cressie, Noel, Catherine a Calder, James S. Clark, Jay M. Ver Hoef, and
Christopher K. Wikle. 2009. ``Accounting for Uncertainty in Ecological
Analysis: the Strengths and Limitations of Hierarchical Statistical
Modeling.'' \emph{Ecological Applications} 19 (3) (apr): 553--70.
doi:10.1890/07-0744.1.
\url{http://www.ncbi.nlm.nih.gov/pubmed/19425416}.

@@

Kocijan, Juš, Agathe Girard, Bla\textbackslash{}vz Banko, and Roderick
Murray-Smith. 2005. ``Dynamic Systems Identification with Gaussian
Processes.'' \emph{Mathematical and Computer Modelling of Dynamical
Systems} 11 (4): 411--424. doi:10.1080/13873950500068567.
\url{http://www.tandfonline.com/doi/abs/10.1080/13873950500068567}.

@@

>>>>

We develop these concerns in the context of fisheries, though the
underlying challenges and methods are germane to many other conservation
and resource management problems. The economic value and ecological
concern have made marine fisheries the crucible for much of the founding
work (H. S. Gordon 1954; Reed 1979; May et al. 1979; Ludwig and Walters
1982) in managing ecosystems under uncertainty. Global trends (Worm et
al. 2006) and controversy (Hilborn 2007; Worm et al. 2009) have made
understanding these challenges all the more pressing.

Uncertainty enters the decision-making process at many levels: intrinsic
stochasticity in biological processes, measurements, and implementation
of policy (\emph{e.g.} Reed 1979; Clark and Kirkwood 1986; Roughgarden
and Smith 1996; Sethi et al. 2005), parameteric uncertainty (\emph{e.g.}
Ludwig and Walters 1982; Hilborn and Mangel 1997; McAllister 1998;
Schapaugh and Tyre 2013), and model or structural uncertainty
(\emph{e.g.} B. K. Williams 2001; Cressie et al. 2009; Athanassoglou and
Xepapadeas 2012). Of these, structural uncertainty incorporates the
least a priori knowledge or assumptions and is generally the hardest to
quantify. Typical approaches assume a weak notion of model uncertainty
in which the correct model (or reasonable approximation) of the dynamics
must be identified from among a handful of alternative models. Here we
consider an approach that addresses uncertainty at each of these levels
without assuming the dynamics follow a particular (i.e.~parametric)
structure.

\emph{Cut the next three paragraphs, since they are covered more
consisely in the above paragraph?}

\paragraph{Process, measurement, and implementation
error}\label{process-measurement-and-implementation-error}

Resource management and conservation planning seek to determine the
optimal set of feasible actions to maximize the value of some objectives
(see ({\textbf{???}})). Process error, measurement error, implementation
error (Reed 1979). These sources of stochasticity in turn mean that
model parameters can only be estimated approximately, requiring
parametric uncertainty also be considered (Ludwig and Walters 1982).

\paragraph{Parametric uncertainty}\label{parametric-uncertainty}

As the parameter values for these models must be estimated from limited
data, there will always be some uncertainty associated with these
values. This uncertainty further compounds the intrinsic variability
introduced by demographic or environmental noise. The degree of
uncertainty in the parameter values can be inferred from the data and
reflected in the estimates of the transition probabilities
({\textbf{???}}; Mangel and Clark 1988; {\textbf{???}}; Schapaugh and
Tyre 2013).

\paragraph{Structural (model)
uncertainty}\label{structural-model-uncertainty}

Estimates of parameter uncertainty are only as good as the parametric
models themselves. Often we do not understand the system dynamics well
enough to know if a model provides a good approximation over the
relevant range of states and timescales (criteria that we loosely refer
to as defining the ``right'' or ``true'' model.) So called structural or
model uncertainty is a more difficult problem than parametric
uncertainty. Typical solutions involve either model choice, model
averaging, or introducing yet greater model complexity of which others
may be special cases (model averaging being one such way to construct
such a model) (B. K. Williams 2001; Athanassoglou and Xepapadeas 2012;
Cressie et al. 2009). Even setting aside other computational and
statistical concerns (e.g. (Cressie et al. 2009)), these approaches do
not address our second concern - representing uncertainty outside the
observed data range.

Model uncertainty is particularly insidious when model predictions must
be made outside of the range of data on which the model was estimated.
This extrapolation uncertainty is felt most keenly in decision-theoretic
(or optimal control) applications, since (a) exploring the potential
action space typically involves considering actions that may move the
system outside the range of observed behavior, and (b)
decision-theoretic alogrithms rely not only on reasonable estimates of
the expected outcomes, but depend on the weights given to all possible
outcomes (\emph{e.g.} Weitzman 2013). If we are observing the
fluctuations of a given fish stock over many years under a fixed
harvesting pressure, we might develop and test a model that could
reasonably predict the frequency of a deviation of a given size, even
when such a deviation has not been previously observed. Yet such
predictions are far less reliable when extrapolated to a harvest
pressure that has not yet been observed. Thus, model uncertainty can be
particularly challenging in the management and decision-making context.

This difficult position of having neither the true model nor data that
covers the full range of possible states is unfortunately the rule more
than the exception. The potential concern of tipping points in
ecological dyanmics (Scheffer et al. 2001; Polasky et al. 2011) reflects
these concerns -- as either knowledge of the true model or more complete
sampling of the state space would make it easy to identify if a tipping
point existed. If we do not know but cannot rule out such a possibility,
then we face decision-making under this dual challege of model
uncertainty and incomplete data coverage.

These dual concerns pose a substantial challenge to existing
decision-theoretic approaches (Brozović and Schlenker 2011). Because
intervention is often too late after a tipping point has been crossed
(but see Hughes et al. (2013)), management is most often concerned with
avoiding potentially catastrophic tipping points before any data is
available at or following a transition that would more clearly reveal
these regime shift dynamics (e.g. Bestelmeyer et al. 2012).

@@

@@

This non-parametric property -- having a structure explicitly dependent
on the data -- is precisely the property that makes this approach
attractive in face of the limited data sampling challenges discussed
above. Having fit a parametric model to some data, the model is
completely described by the values (or posterior distributions) of it's
parameters. The non-parametric model is not captured by its parameter
values or distributions alone. Either the model scales with the
complexity of the data on which it is estimated (e.g.~nonparametric
heirarchical approaches such as the Dirchlet process) or the data points
become themselves part of the model specification, as in the
nonparametric regression used here.

The use of Gaussian process (GP) regression (or ``kriging'' in the
geospatial literature) to formulate a predictive model is relatively new
in the context of modeling dynamical systems ({\textbf{???}}), and was
first introduced in the context ecological modeling and fisheries
management in Munch et al. (2005). An accessible and thorough
introduction to the formulation and use of GPs can be found in Rasmussen
and Williams (2006).

@@

\% latex table generated in R 3.0.2 by xtable 1.7-1 package \% Mon Nov
18 14:39:35 2013

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/nonparametric-bayes-out_of_sample_predictions.pdf}
\caption{Out of sample predictions of the dynamics under each model.
Points show the stock size simulated by the true model. Overlay shows
the range of states predicted by each model, based on the state observed
in the previous time step. The Ricker model always predicts population
growth, while the actual population shrinks in each step as the initial
condition falls below the Allee threshold of the underlying model
(Allen). Note that the GP is both more pessimistic and more uncertain
about the future state than the parameteric models, while the realized
state often falls outside of the expected range forecasted by the
structurally incorrect Myers and Ricker models.}
\end{figure}

@@

Cressie, Noel, Catherine a Calder, James S. Clark, Jay M. Ver Hoef, and
Christopher K. Wikle. 2009. ``Accounting for Uncertainty in Ecological
Analysis: the Strengths and Limitations of Hierarchical Statistical
Modeling.'' \emph{Ecological Applications : a Publication of the
Ecological Society of America} 19 (3) (apr): 553--70.
\url{http://www.ncbi.nlm.nih.gov/pubmed/19425416}.

@@

@@

Polasky, Stephen, Stephen R. Carpenter, Carl Folke, and Bonnie Keeler.
2011. ``Decision-making Under Great Uncertainty: Environmental
Management in an Era of Global Change.'' \emph{Trends in Ecology \&
Evolution} (may): 1--7. doi:10.1016/j.tree.2011.04.007.
\url{http://www.ncbi.nlm.nih.gov/pubmed/21616553}.
